Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-06-11 paper.tex
Submit to PNAS

% Created 2018-09-26 Wed 21:07
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{lineno}
\usepackage{todonotes}
\usepackage{times}

@@

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
%% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

\newpage{}

% \section{Introduction}
% \label{sec:org2ea169d}
\linenumbers{}

{\bfseries The dielectric constant, which defines the polarization of
  the media, is a key quantity in condensed matter. It determines
  several electronic and optoelectronic properties important for a
  plethora of modern technologies from computer memory to field effect
  transistors and communication circuits. Moreover, the importance of
  the dielectric constant in describing electromagnetic interactions
  through screening plays a critical role in understanding fundamental
  molecular interactions. Here we show that despite its fundamental
  transcendence, the dielectric constant does not define unequivocally
  the dielectric properties of two-dimensional (2D) materials due to
  the locality of their electrostatic screening. Instead, the electric
  polarizability correctly captures the dielectric nature of a 2D
  material which is united to other physical quantities in an
  atomically thin layer. We reveal a long-sought universal formalism
  where electronic, geometrical and dielectric properties are
  intrinsically correlated through the polarizability opening the door
  to probe quantities yet not directly measurable including the real
  covalent thickness of a layer. We unify the concept of dielectric
  properties in any material dimension finding a global dielectric
  anisotropy index defining their controllability through
  dimensionality.  }

The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgaps\cite{Moss_1950_relation,Moss_1985_n_Eg}, 
optical absorption\cite{kittel_2005_introduction} and 
conductivities\cite{Dressel_2001_electrodynamics}   
with elemental interactions. 
The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an 
electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
condensed matter physics, as well as in related fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
theoretical and experimental techniques of distinct flavors where the probe of the dielectric properties 
is made through an external electric field. 
%
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
electronic and dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
The confined nature of the electrons in such atomically thin space associated with the 
attenuated and anisotropic character of the dielectric screening of 2D crystals 
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant 
may represent their dielectric features or it can be used only as an 
additional parameter from the bulk-counterparts.

@@

@@

@@

We have also searched for additional relations between the 2D
polarizabilities with other physical quantities, including the
effective carrier mass, quantum capacitance (density of states) and
total atomic polarizabilities with no apparent correlations being
found (Supplementary Section \ref{SI-sec:gpaw-3}).  We found however that
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} have a natural
connection with the screening properties of the layer.
%
In merit of the unit analysis, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ both have unit of
$4\pi\varepsilon_{0} \cdot$[Length]. In other words,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
represent in- and out-of-plane characteristic lengths,
respectively. It is well-known that the in-plane screened
electrostatic potential $V(r)$ from a point charge as a function of
distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
    \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulomb potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively. This is analog to the polarizability ellipsoid picture
of molecules used in spectroscopy \cite{Banwell_1994} (see
Supplementary Figure \ref{SI-fig:ellipsoid}). The polarizability
ellipsoid for a 2D material is in general ultra flat, with
$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
TMDCs in Table \ref{tbl:radii}.  Moreover, $r_{0}^{\parallel}$ is
generally larger for a smaller bandgap semiconductor, which
qualitatively explains the inverse proportional relation between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$ seen in
Eq. \ref{eq:2D-Moss-para}.  This gives a geometrical interpretation of
the bandgap in terms of the screening radius of the layer.

%\subsection{Bridging the 2D and 3D Dielectric Properties}
%\label{sec:2D-3D}

We next show that the underlying physical mechanism linking 
polarizability to bandgaps allows us to further bridge 
the dielectric properties between 2D materials and 
their 3D bulk counterparts in a remarkable way. 
%The dielectric constant $\varepsilon$, although not well-defined for
%a monolayer 2D material, becomes applicable when the 2D layers are
%stacked. 
%
%
%
In a bulk layered material stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of the bulk layered material can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\textbf a}) as:
%
%
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
%
%
Here we neglect the effect of the stacking order of the layers.  The
dielectric constant $\varepsilon$ although not well-defined for a
monolayer 2D material becomes applicable when the 2D layers are put
together.
%
We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (\textit{y}-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(\textit{x}-axis) as shown in Figure \ref{fig-4}{\textbf b} and \ref{fig-4}{\textbf c}. 
Both HSE06 and PBE datasets give almost identical results.  
%
We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} are in good agreement with a linear
regression slope of 1.01 and $R^2$ of 0.97. Conversely,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The above results indicate that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to the interlayer coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. 
%With a better model describing
%$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
%the degree of interlayer coupling, the dielectric transition from 2D
%to 3D would be smoothly described.

>>>>

% Created 2018-09-26 Wed 21:07
% Intended LaTeX compiler: pdflatex
% \documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=false]{achemso}
\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

\templatetype{pnasresearcharticle} % Choose template 
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{lineno}
\usepackage{todonotes}
\usepackage{times}

@@

\title{Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}

\author[a,1]{Tian Tian}
\author[b, 1]{Declan Scullion}
\author[b]{Dale Hughes}
\author[c]{Lu Hua Li}

\author[a]{Chih-Jen Shih}
\author[d]{Jonathan Coleman}
\author[e]{Manish Chhowalla}
%% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}

\author[b, 2]{Elton J. G. Santos}

\leadauthor{Tian}

\affil[a]{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\affil[b]{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\affil[c]{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\affil[d]{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\affil[e]{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}

\authorcontributions{E.J.G.S. designed the scope of research. T.T.,
  D.S. and D.H. performed first-principles calculations. T.T. and
  D.S. performed the analysis of data. T.T., D.S. and E.J.G.S. wrote
  the paper. L.H.L., C.J.S., J.C. amd M.C. participated in discussion of manuscript.}
\authordeclaration{The authors declare no conflict of interest.}
\equalauthors{\textsuperscript{1}T.T. and D.S. contributed equally to this work}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: e.santos@qub.ac.uk}

% \significancestatement{

% }

\begin{abstract}
  The dielectric constant, which defines the polarization of
  the media, is a key quantity in condensed matter. It determines
  several electronic and optoelectronic properties important for a
  plethora of modern technologies from computer memory to field effect
  transistors and communication circuits. Moreover, the importance of
  the dielectric constant in describing electromagnetic interactions
  through screening plays a critical role in understanding fundamental
  molecular interactions. Here we show that despite its fundamental
  transcendence, the dielectric constant does not define unequivocally
  the dielectric properties of two-dimensional (2D) materials due to
  the locality of their electrostatic screening. Instead, the electric
  polarizability correctly captures the dielectric nature of a 2D
  material which is united to other physical quantities in an
  atomically thin layer. We reveal a long-sought universal formalism
  where electronic, geometrical and dielectric properties are
  intrinsically correlated through the polarizability opening the door
  to probe quantities yet not directly measurable including the real
  covalent thickness of a layer. We unify the concept of dielectric
  properties in any material dimension finding a global dielectric
  anisotropy index defining their controllability through
  dimensionality.  
\end{abstract}

\dates{This manuscript was compiled on \today}

\begin{document}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% \section{Introduction}
% \label{sec:org2ea169d}
% \linenumbers{}

\dropcap{T}he dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgaps\cite{Moss_1950_relation,Moss_1985_n_Eg}, 
optical absorption\cite{kittel_2005_introduction} and 
conductivities\cite{Dressel_2001_electrodynamics}   
with elemental interactions. 
The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an 
electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
condensed matter physics, as well as in related fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
theoretical and experimental techniques of distinct flavors where the probe of the dielectric properties 
is made through an external electric field. 
%
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
electronic and dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
The confined nature of the electrons in such atomically thin space associated with the 
attenuated and anisotropic character of the dielectric screening of 2D crystals 
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant 
may represent their dielectric features or it can be used only as an 
additional parameter from the bulk-counterparts.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{img/fig1.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha_{\mathrm{2D}}^{\parallel}$ and
  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.
  % HSE06 functional is used in all plots.
}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=9cm]{img/fig2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D materials}. \textbf{a}. The structures of
  the 2D materials investigated in this
  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
  (blue dots) for all the 2D materials studied.
  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. HSE06 functional is used to obtain the data. \textbf{c}.
  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the background. \textbf{d}.
  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
  in the inset), showing a perfect linear relation with slope very
  close to $1/4\pi$ (i.e.
  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
  revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
  as superimposed on \textbf{c} and \textbf{d}.}
\end{figure}

@@

We have also searched for additional relations between the 2D
polarizabilities with other physical quantities, including the
effective carrier mass, quantum capacitance (density of states) and
total atomic polarizabilities with no apparent correlations being
found (Supplementary Section \ref{SI-sec:gpaw-3}).  We found however that
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} have a natural
connection with the screening properties of the layer.
%
In merit of the unit analysis, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ both have unit of
$4\pi\varepsilon_{0} \cdot$[Length]. In other words,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
represent in- and out-of-plane characteristic lengths,
respectively. It is well-known that the in-plane screened
electrostatic potential $V(r)$ from a point charge as a function of
distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
    \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulomb potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively. This is analog to the polarizability ellipsoid picture
of molecules used in spectroscopy \cite{Banwell_1994} (see
Supplementary Figure \ref{SI-fig:ellipsoid}). The polarizability
ellipsoid for a 2D material is in general ultra flat, with
$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
TMDCs in Table \ref{tbl:radii}.  Moreover, $r_{0}^{\parallel}$ is
generally larger for a smaller bandgap semiconductor, which
qualitatively explains the inverse proportional relation between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$ seen in
Eq. \ref{eq:2D-Moss-para}.  This gives a geometrical interpretation of
the bandgap in terms of the screening radius of the layer.
\begin{table}
  \centering
  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
    selected 2D materials calculated from first principles
    simulations. $r_{0}^{\parallel}$ is in general much larger than
    $r_{0}^{\perp}$, which accounts for the highly anisotropic
    dielectric nature of 2D materials.}
  \label{tbl:radii}  
  \begin{tabular}{lcc}
    \hline
    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
    \hline
    2H-MoS$_{2}$ & 40.0 & 2.50 \\
    2H-MoSe$_{2}$ & 45.5 & 2.72  \\
    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
    2H-WS$_{2}$ & 35.7 & 2.46  \\
    2H-WSe$_{2}$ & 41.0 & 2.71 \\
    2H-WTe$_{2}$ & 53.5 &  3.17\\
    \hline
  \end{tabular}
\end{table}

%\subsection{Bridging the 2D and 3D Dielectric Properties}
%\label{sec:2D-3D}
\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha_{\mathrm{2D}}^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) functionals.}
\end{figure}
We next show that the underlying physical mechanism linking 
polarizability to bandgaps allows us to further bridge 
the dielectric properties between 2D materials and 
their 3D bulk counterparts in a remarkable way. 
In a bulk layered material stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of the bulk layered material can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\textbf a}) as:
%
%
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
%
%
Here we neglect the effect of the stacking order of the layers.  The
dielectric constant $\varepsilon$ although not well-defined for a
monolayer 2D material becomes applicable when the 2D layers are put
together.
%
We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (\textit{y}-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(\textit{x}-axis) as shown in Figure \ref{fig-4}{\textbf b} and \ref{fig-4}{\textbf c}. 
Both HSE06 and PBE datasets give almost identical results.  
%
We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} are in good agreement with a linear
regression slope of 1.01 and $R^2$ of 0.97. Conversely,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The above results indicate that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to the interlayer coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. 
%With a better model describing
%$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
%the degree of interlayer coupling, the dielectric transition from 2D
%to 3D would be smoothly described.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{img/fig5.pdf}
  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
      function of bandgap $E_{\mathrm{g}}$}. The
    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
    their bulk counterparts (orange square) can be distinguished by
    the line $\eta=0.048(E_{\mathrm{g}}/\mathrm{eV})+0.087$. $\eta-E_{\mathrm{g}}$ values of
    semiconducting materials in other dimensions are also superimposed
    for comparison. Isotropic dielectric property is observed for bulk
    covalent materials (3D, red triangle) and fullerenes (0D, green
    star), while reduced dimensional materials, including planar
    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
    scattered along the boundary line. The dimensionality and
    structure of typical materials are shown along the axis on the
    right. Compared with other materials, 2D materials and their bulk
    counterparts provide more flexibility of controlling the
    dielectric anisotropy.}
  \label{fig:aniso}
\end{figure}
Finally, we show that a general picture of the dielectric properties in
any dimension can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha_{\mathrm{2D}}^{ii}}{\alpha_{\mathrm{2D}}^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangles) can be
clearly distinguished from the bulk layered materials (orange squares)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as the electrostatic
transparency phenomena\cite{Liluhua_2014,Tian_2016,Li_2018} and the large exciton
binding energies
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy
index of corresponding 2D layer (see additional details in
Supplementary Section \ref{SI-sec:aniso}), which is the basis for the
separation of bulk and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase
diagram.  For comparison, we also superimpose the dielectric
anisotropy indices of common semiconducting materials in other
dimensions (details see Supplementary Section \ref{SI-sec:aniso}) on
the phase diagram in Figure \ref{fig:aniso}. Bulk covalent (3D,
e.g. Si, GaN) and 0D (fullerenes) semiconductors show isotropic
dielectric properties, scattered on the line $\eta=1$. On the other
hand, reduced dimensionality increases the dielectric anisotropy of
materials such as planar organic semiconductor (OSc, 1D-2D,
e.g. CuPc), carbon nanotube (CNT, 1D), linear OSc (0D-1D,
e.g. polyacene and polyacetylene). Interestingly, most of these
materials also scatter along the boundary line separating the bulk and
2D regimes, indicating the criteria distinguishing 2D (more
anisotropic) and bulk layered materials (more isotropic) from the
$\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
dimensions. From the phase diagram, we can see that 2D and bulk
layered materials (also including 2D van der Waals heterostructure
(vdWH) \cite{Novoselov_2016}), provides more flexibility in
controlling the dielectric and electronic properties, compared with
semiconductors in other dimensions.
